Put Title here

### 2018-12-19 General WLD combinatorics.tex
corrected (hopefully) some indexing in some intervals
fixed some notational things in section 2 see higlighted notes

Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $(P, V(P))$.  Conversely, given a subdiagram $(P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$ as follows:
\begin{itemize}
\item The vertex set of the subgraph is
  \begin{itemize}
  \item the vertices of $\tau(W)$ corresponding to edges on which propagators of $P$ are supported
  \item along with any other vertices of $\tau(W)$ for which both neighbours are as described in the previous point.
  \end{itemize}
\item The edge set of the subgraph is
  \begin{itemize}
  \item the edges of $\tau(W)$ corresponding to propagators of $P$
  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set
  \end{itemize}
\end{itemize}
Note that the subgraph only depends on $P$, not the vertex set of the subdiagram, but it is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.

@@

Now suppose that $t$ has $m>2$ vertices.  We count how many edges of $t$ are not on the outer face of $\tau(W)$.  Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ and this subgraph has $m$ vertices. Call this new subgraph $S$, and let $j$ be the number of connected components of $S$.   To join the components of $S$ into the outer face of $t$, $t$ must have $j$ edges in its outer face which are not in the outer face of $\tau(W)$.  Furthermore $t$ has $m-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.  Thus there are $m-3+j$ edges of $t$ not in the outer face of $\tau(W)$.

@@

Suppose $|P|=1$. Let $p$ be the element of $P$. The exactness condition on $(P, V(P))$ says that the four supporting vertices of $p$ are distinct.  If the support of $p$ is four consecutive vertices, then the ends of the edge corresponding to $p$ in $\tau(W)$ have a common neighbour and so $t$ is a single triangle, hence a triangulated piece.  If the support of $p$ is not four consecutive vertices, then the vertices which are the ends of $t$ are separated by at least two vertices along the cycle.  This implies that $t$ is a trivial triangulated piece.

@@

To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.

@@

Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.

@@

\begin{lem}\label{lem properties of prop flats}
Let $F(P)$ be a propagator flat as defined above. Then
\begin{enumerate}
\item $F(\emptyset)$ is exactly the set of vertices which support no propagators, while for $P \neq \emptyset$ we have \[F(P) = \big(V(P) \setminus V(P^c)\big) \cup F(\emptyset).\] \note{updated (1) to match new definition of $F(P)$; }
\item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
\end{enumerate}
\end{lem}
\begin{proof}
The proof of (1) and (2) are routine applications of the definition and are omitted.

>>>>

Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.  Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
\begin{itemize}
\item The vertex set of the subgraph $t$ is
  \begin{itemize}
  \item \hlfix{the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$}{changed to simplify with existing notation, but now it contradicts below}
  \end{itemize}
\item The edge set of the subgraph is
  \begin{itemize}
  \item the edges of $\tau(W)$ corresponding to propagators of $P$
  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set
  \end{itemize}
\end{itemize}
Note that the subgraph $t$ only depends on $P$, \hlfix{not the vertex set of the subdiagram $W_P$}{really? why?}, but it is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.

@@

Now suppose that $t$ has $m>2$ vertices.  We count how many edges of $t$ are not on the outer face of $\tau(W)$.  These are exactly the edges of $t$ defined by propagators of $W$. Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ and this subgraph has $m$ vertices. Call this new subgraph $S$, and let $j$ be the number of connected components of $S$.   To join the components of $S$ into the outer face of $t$, $t$ must have $j$ edges in its outer face which are not in the outer face of $\tau(W)$.  Furthermore $t$ has $m-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.  Thus there are $m-3+j$ edges of $t$ not in the outer face of $\tau(W)$.

@@

Suppose $|P|=1$. Let $p$ be the element of $P$. The exactness condition on $(P, V(P))$ says that the four supporting vertices of $p$ are distinct.  If the support of $p$ is four consecutive vertices, then $V(p)$ defines three consecutive boundary edges of $W$, so $t$ is a single triangle, hence a triangulated piece.  If the support of $p$ is not four consecutive vertices, then the vertices which are the ends of $t$ are separated by at least two vertices along the cycle.  This implies that $t$ is a trivial triangulated piece.

@@

To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V(q))$, for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.

@@

Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely. In particular, we show that the matroids associated to exact subdiagrams are uniform (Theorem \ref{??}) and that

@@

\begin{lem}\label{lem properties of prop flats} \sanote{do we need the first 2? They follow directly from the definition 1.2. Do we use them later?}
Let $F(P)$ be a propagator flat as defined above. Then
\begin{enumerate}
\item $F(\emptyset)$ is exactly the set of vertices which support no propagators, while for $P \neq \emptyset$ we have \[F(P) = \big(V(P) \setminus V(P^c)\big) \cup F(\emptyset).\] \note{updated (1) to match new definition of $F(P)$; }
\item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
\end{enumerate}
\end{lem}
\begin{proof}
The proof of (1) and (2) are routine applications of the definition and are omitted.
